Trends of downward SDR in Thessaloniki 

### 2023-04-24 Article.Rmd
Commit 2023-04-24 21:17

We can separate the data preparation in three parts, ..........

<!-- measurement -->
For both CM-21 and CHP-1 instruments, the mean signal and the standard deviation over one minute is recorded every one minute.
<!-- screening -->
A manual screening processes, removes inconsistencies and erroneous recordings, that can occur on a long contentious operation, like this one.
<!-- physical quantities -->
The conversion to irradiance was done using the available calibrations factors. For CHP-1, there is only the initial one by the manufacture, and for CM-21 there are seven calibration procedure in the span of the period we investigate.
<!-- Dark signal -->
We have adjusted the measurements for the dark signal offset, by a daily value, using the nights before and after each day.
<!-- Quality assurance -->
A radiation data quality assurance procedure was applied, adjusted for the site, based on methods of Long and Shi\ [-@long_automated_2008; -@Long2006]. Only data characterized as good quality were used in this study.
<!-- Data selection -->
Due to larger measurement uncertainty near the horizon, we exclude
all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we remove data with Azimuth angle between 
$35^\circ$ and $120^\circ$ and SZA greater than $80^\circ$. At 
those cases the Sun, were not visible by the instruments.

>>>>

We can separate the data preparation in three parts, a) the acquisition of radiation measurements from the sensor, b) a radiation data quality check, and c) the identification of "clear sky" conditions from the radiometric data.

### Acquisition of radiometric data.

<!-- measurement -->
We sample the signal of the CM-21 pyranometer with a rate of $1 {Hz}$, and record the average signal and the standard deviation over each minute of the hour. The measurements are corrected for the zero offset of the instrument, using the "dark signal" (Sun elevation bellow $10\circ$, for a period of

<!-- screening -->
A manual screening processes, removes inconsistencies and erroneous recordings, that can occur on a long contentious operation, like this one.
<!-- physical quantities -->
The conversion to irradiance was done using the available calibrations factors. For CHP-1, there is only the initial one by the manufacture, and for CM-21 there are seven calibration procedure in the span of the period we investigate.
<!-- Dark signal -->
We have adjusted the measurements for the dark signal offset, by a daily value, using the nights before and after each day.
<!-- Quality assurance -->
A radiation data quality assurance procedure was applied, adjusted for the site, based on methods of Long and Shi\ [-@long_automated_2008; -@Long2006]. Only data characterized as good quality were used in this study.
<!-- Data selection -->
Due to larger measurement uncertainty near the horizon, we exclude
all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we remove data with Azimuth angle between 
$35^\circ$ and $120^\circ$ and SZA greater than $80^\circ$. At 
those cases the Sun, were not visible by the instruments.
